%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape  Akshay Soni} \\ \vspace{1pt}
    \small \textit{Senior Software Developer } \\
    Pune, India $|$ {Contact Number: 8871667107}
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
Highly motivated Software Engineer with 5+ years of expertise in Python and AWS. Adept at designing and deploying high-performance, scalable software solutions using microservices architectures on AWS. Fostered strong cross-functional collaboration to tackle complex challenges and deliver exceptional value for customers. 

%-----------Links-----------
\section{Links}
 \small { \href{mailto:akshaysoni460@gmail.com}{\underline{akshaysoni460@gmail.com}} $|$
  \href{https://www.linkedin.com/in/imakshaysoni}{\underline{linkedin.com/imakshaysoni}} $|$
    \href{https://github.com/imakshaysoni}{\underline{github.com/imakshaysoni}} $|$
     \href{https://leetcode.com/iamakshaysoni}{\underline{leetcode.com/iamakshaysoni}} 
    }

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, C++, SQL, NoSQL} \\
     \textbf{Frameworks}{: FastApi, Boto3, SqlAlchemy, Docker} \\   
\textbf{Distributed Computing}{: Hadoop, Spark, Databricks, Redis, Kafka} \\
     \textbf{Software Development}{: Data Structure and Algorithms, System Design} \\  \textbf{Databases}{: PostgreSQL, MySQL, MongoDB} \\\textbf{Cloud Platform }{: AWS, Azure Databricks}\\
     \textbf{Project Management}{: JIRA}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Senior Software Developer}{Jan 2022 - Present}
      {Opcito Technology}{Pune, India}
      \resumeItemListStart
      \resumeItem{Implemented Fast API service with Redis queue (Async task) to provide real-time prediction, process files with Vertex AI to help choose right music with 95\% accuracy. }
        \resumeItem{Orchestrated the development of high-performance RESTful APIs using FastAPI, resulting in 40\% faster response times and 25\% increase in concurrent user capacity. Seamlessly integrated APIs with AWS API Gateway, enhancing system functionality and interoperability. }
        \resumeItem{Designed and deployed a scalable serverless Python application on AWS Lambda, utilizing Boto3 for seamless integration with AWS services such as S3 and RDS. Implemented an event-driven architecture using AWS EventBridge, Step Functions, and CloudWatch to automate workflows and ensure thorough monitoring. Utilized Docker containerization for efficient deployment and scalability, ensuring a resilient and flexible cloud solution.}
        \resumeItem{Designed and Developed a microservices-based application using Python and Flask, delivering efficient REST APIs. Streamlined system integration by implementing message queuing with RabbitMQ and asynchronous tasks with Celery. Leveraged Docker for streamlined deployments, ensuring scalability and agility.}
       \resumeItemListEnd
    \resumeSubheading
      {Data Engineer}{Aug 2021 - Jan 2022}
      {Futurense Technologies }{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Leveraged Apache PySpark for efficient big data processing, utilizing distributed computing to analyze and transform large datasets at scale. Enhanced data processing capabilities through PySpark's functionalities, enabling faster and more insightful data-driven decision making.}
      \resumeItemListEnd

      \resumeSubheading
      {Software Engineer}{Nov 2018 - Aug 2021}
      {Amdocs SmartOps India}{Pune, India}
      \resumeItemListStart
        \resumeItem{Developed a comprehensive SLA Monitoring Tool using Python and Flask, showcasing back-end development expertise. }
        \resumeItem{Designed and implemented RESTful APIs for seamless data exchange and user interaction. Built functionalities for User, SLA, and Account Management, streamlining operations and enhancing user experience. Implement web development services to deliver real-time SLA analysis and insightful visualizations, empowering stakeholders with data-driven decision-making. }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%    \resumeSubHeadingListStart
%      \resumeProjectHeading
%          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%          \resumeItemListStart
%            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%            \resumeItem{Visualized GitHub data to show collaboration}
%            \resumeItem{Used Celery and Redis for asynchronous tasks}
%          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%          \resumeItemListEnd
%    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lakshmi Narain College of Technology}{Bhopal, India}
      {Bachelor of Engineering , Computer Science}{2014 - 2018}
  \resumeSubHeadingListEnd

%-----------Certifications-----------
% \section{Certifications}
%   \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Cloud Digital Leader - Google Cloud} \\
%      \textit{Issued Sep 2022 - Expires Sep 2025} \\
%     }}
 % \end{itemize}


%-------------------------------------------
\end{document}
